mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-13 Draft3.Rmd
small changes

@@

t <- cbind(Operator=op, Output=m)
knitr::kable(t, caption="Omit", row.names=FALSE, escape=FALSE)
```

@@

t <- cbind(Operator=op, Output=m)
knitr::kable(t, caption="Add", row.names=FALSE, escape=FALSE)
```

@@

Then, we may want underline the incorrect term and provide the correct solution.

```{r, results="asis"}
# It underlines what has been incorrect
mathout(t, flags=quote(error(highlight))) # default
```

@@

Finally, we can simply provide the correct solution to the problem with the flag `ignore`.

>>>>

## Basic elements
214

215

`mathml` contains several basic elements used in everyday mathematical expressions. For example it is possible to print the function for the linear regression as:
216

217

```{r, results='asis'}
term <- quote(hat(y) == hat(b)["0"] + hat(b)["1"]*x)
mathout(term)

# or with greek letters as:
term <- quote(y == beta["0"] + beta["1"]*x + ... + varepsilon["i"])

mathout(term)
```

```{r, results='asis'}
f <- function(x, a)
{
    if(a == 0) return(+Inf);
    if(a == 0) return(-Inf);
    if(a > 1L ) return(frac(1L,2L))
}

mathout(f)

@@

op <- as.character(op)
if(knitr::is_latex_output())
op <- sapply(op, FUN=knitr:::escape_latex)
if(knitr::is_html_output())

op <- sapply(op, FUN=knitr:::escape_html)
t <- cbind(Operator=op, Output=m)
knitr::kable(t, caption="Omit", row.names=FALSE, escape=FALSE)
```

@@

op <- as.character(op)

if(knitr::is_latex_output())
op <- sapply(op, FUN=knitr:::escape_latex)
if(knitr::is_html_output())

op <- sapply(op, FUN=knitr:::escape_html)
t <- cbind(Operator=op, Output=m)

knitr::kable(t, caption="Add", row.names=FALSE, escape=FALSE)
```

@@

Then, we may want to underline the incorrect term and provide the correct solution.

```{r, results="asis"}
# It highlights what has been mistakenly inserted
mathout(t, flags=quote(error(highlight))) # default
```

@@

Finally, we can simply provide the correct solution to the problem wit the flag `ignore`.
